POMDP comparisons across sigma_m, sigma_g

### 2017-12-28 appendix/appendix.Rmd
run longer

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.2), 
                    sigma_m = c(0, 0.1, 0.2),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
log_dir <- "appendix_alphas" # Store the computed solution files here
meta
```

@@

```{r eval=TRUE}
dir.create(log_dir)

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir) %>% left_join(meta) %>% arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
```

>>>>

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.15), 
                    sigma_m = c(0, 0.1, 0.15),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
log_dir <- "appendix_alphas" # Store the computed solution files here
meta
```

@@

```{r eval=FALSE}
dir.create(log_dir)
options(mc.cores=2)

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir) %>% 
  mutate(scenario = as.character(scenario)) %>%
  left_join(meta) %>% arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
```
